Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination

### 2024-09-30 manuscript/manuscript.Rmd
Three studies

@@

# Load necessary library
library(ggplot2)
library(dplyr)
library(tidyr)

# Reshape the data to long format
study2_long <- study2_time3 %>%
  pivot_longer(cols = c(likable, warmAvg), 
               names_to = "Metric", 
               values_to = "Value")

# Create the plot
ggplot(study2_long, aes(x = Advice, y = Value, color = Metric)) +  
  # Add points for each observation
  geom_point(size = 2, alpha = 0.7) +

  # Add linear regression lines for each metric
  geom_smooth(method = "lm", se = TRUE, aes(fill = Metric), alpha = 0.2, show.legend = FALSE) +

  # Customize axis labels
  scale_y_continuous(name = "Scores",limits = c(0.9, 5.1)) +  
  scale_x_continuous(name = "Advised Rank",limits = c(1, 10), breaks = c(1,2,3,4,5,6,7,8,9,10)) +

>>>>

library(ggplot2)
library(dplyr)
library(tidyr)

@@

# Reshape the data to long format
study2_long <- study2_time3 %>%
  pivot_longer(cols = c(likable, warmAvg), 
               names_to = "Evaluation", 
               values_to = "Value")

# Create the plot
ggplot(study2_long, aes(x = Advice, y = Value, color = Evaluation)) +  
  # Add points for each observation
  geom_point(size = 2, alpha = 0.7) +

  # Add linear regression lines for each metric
  geom_smooth(method = "lm", se = TRUE, aes(fill = Evaluation), alpha = 0.2, show.legend = FALSE) +

  # Customize axis labels
  scale_y_continuous(name = "Evaluation",limits = c(0.9, 5.1)) +  
  scale_x_continuous(name = "Advised Rank",limits = c(1, 10), breaks = c(1,2,3,4,5,6,7,8,9,10)) +
